


This dissertation is based on the following papers (in chronological order). In each work, all authors contributed equally unless stated otherwise.

\begin{itemize}
\item[\cite{Groenland2018}] \textbf{\textit{Many-body strategies for multiqubit gates: Quantum control through Krawtchouk-chain dynamics}} \\
Koen Groenland, Kareljan Schoutens, \\
Phys. Rev. A \textbf{97}, 042321 (2018). \\
\cref{chap:krawtchouk} is based on this paper.
%
%
\item[\cite{Groenland2019}] \textbf{\textit{Adiabatic state distribution using anti-ferromagnetic spin systems}} \\
Koen Groenland, \\
SciPost Phys. \textbf{6}, 011 (2019). \\
\cref{chap:heisenberg} is based on this paper.
%
%
\item[\cite{Groenland2019a}] \textbf{\textit{Quantum gates by resonantly driving many-body eigenstates, with a focus on Polychronakos' model}} \\
Koen Groenland, Kareljan Schoutens, \\
JSTAT \textbf{2019}, 7, 073103 (2019). \\
\cref{chap:pc,chap:gates_intro} are based on this paper.
%
%
\item[\cite{Groenland2019b}] \textbf{\textit{Adiabatic transfer of amplitude using STIRAP-like protocols generalizes to many bipartite graphs}} \\
Koen Groenland, Carla Groenland, Reinier Kramer, \\
Submitted to J. Math. Phys.. \\
\cref{chap:ctap} is based on this paper.
%
%
\item[\cite{Rasmussen2019}] \textbf{\textit{Single-step implementation of high fidelity $n$-bit Toffoli gates}} \\
Stig E. Rasmussen, Koen Groenland, Rene Gerritsma, Kareljan Schoutens,\\ Nikolaj T. Zinner,\\
Submitted to Phys. Rev. A. \\
\cref{chap:star} is based on this work. The first two authors are the main contributors. 
\end{itemize}


